Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex

Within all experiments we used the following existing solvers 
with public available implementation.
\begin{itemize}
    \item 
    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
    Therefore we exclude those in our experiments.
    \item \textbf{KL}\cite{???}  and a public available 
        implementation 
        \footlabel{opengm-master}{%
        %\footnote{
        %    \label{opengm-master} 
            \url{https://github.com/opengm/opengm}
            %\label{opengm-master}
        }
    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
    version of a public available implementation implementation\footref{opengm-master}.
    We replace a highly used queue with a more suitable and
    fast \emph{index-min-heap}\cite{???}.
    MC-R indicates that only the LP is solved, while MC-I solves
    the ILP.
    \item non vision solvers here TODO
\end{itemize}
And the following proposed solvers:
\begin{itemize}
\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
as described in sec.~\ref{sec:ehc}.
\item \textbf{EHC-CGC}: As CGC but warm started 
with the solution from EHC.
\end{itemize}

>>>>

Within all experiments we used the following existing solvers 
with public available implementation.
\begin{itemize}
    \item 
    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
    Therefore we exclude those in our experiments.
    \item \textbf{KL}\cite{???}  and a public available 
        implementation 
        \footlabel{opengm-master}{%
        %\footnote{
        %    \label{opengm-master} 
            \url{https://github.com/opengm/opengm}
            %\label{opengm-master}
        }
    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified

    version of a public available implementation implementation \footref{opengm-master}.

    We replace a highly used queue with a more suitable and
    fast \emph{index-min-heap}\cite{???}.
    MC-R indicates that only the LP is solved, while MC-I solves
    the ILP.
    \item non vision solvers here TODO
\end{itemize}
And the following proposed solvers:
\begin{itemize}
\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
as described in sec.~\ref{sec:ehc}.
\item \textbf{EHC-CGC}: As CGC but warm started 
with the solution from EHC.
\end{itemize}
